TRIK Studio: Technical Introduction

### 2017-06-06 2017-trikStudioEnglishExtended/trikStudioEnglishExtended.tex
Added extended article with Terekhov's addition

\documentclass[conference]{IEEEtran}

@@

\author{
	\IEEEauthorblockN{Dmitry Mordvinov}
	\IEEEauthorblockA{
		St.-Petersburg State University \\
		St.Petersburg, Russia \\
		dmitry.mordvinov@se.math.spbu.ru
	}
\and
	\IEEEauthorblockN{Yurii Litvinov}
	\IEEEauthorblockA{
		St.-Petersburg State University \\
		St.Petersburg, Russia \\
		y.litvinov@spbu.ru
	}
\and
	\IEEEauthorblockN{Timofey Bryksin}
	\IEEEauthorblockA{
		St.-Petersburg State University \\
		St.Petersburg, Russia \\
		t.bryksin@spbu.ru
	}
}

@@

@@

\bibliographystyle{IEEEtran}
\bibliography{trikStudioEnglish}

>>>>

% Extended version of FRUCT20 article for International Journal of Embedded and Real-Time Communication Systems (IJERTCS)
\documentclass[conference]{IEEEtran}

@@

\author{
	\IEEEauthorblockN{Dmitry Mordvinov}
	\IEEEauthorblockA{
		St.-Petersburg State University \\
		St.Petersburg, Russia \\
		dmitry.mordvinov@se.math.spbu.ru
	}
\and
	\IEEEauthorblockN{Yurii Litvinov}
	\IEEEauthorblockA{
		St.-Petersburg State University \\
		St.Petersburg, Russia \\
		y.litvinov@spbu.ru
	}
\and
	\IEEEauthorblockN{Timofey Bryksin}
	\IEEEauthorblockA{
		St.-Petersburg State University \\
		St.Petersburg, Russia \\
		t.bryksin@spbu.ru
	}
\and
	\IEEEauthorblockN{Andrey Terekhov}
	\IEEEauthorblockA{
		St.-Petersburg State University \\
		St.Petersburg, Russia \\
		a.terekhov@spbu.ru
	}
}

@@

\section{Graphic language for real time system}
\label{chapter:realTime}
Our team has been implementing real time systems since 1980. We started when we were charged to develop Automatic Digital Exchange Stations. Exchange system is a complicated object which includes exchange equipment, several control computers which are connected among and with exchange system equipment. All the fragments of the system have to work fast (if one of the system fragments is out of time restriction an important information may be lost) and safe (many of real-time systems are related to the mission critical class of systems). Switch software must not only control the exchange system but also includes database and interface with an operator. That’s why real time systems are related to one of the most complicated object from the point of its implementation.

Graphic real-time model consists of 3 diagram types: 
\begin{enumerate}
	\item Function diagram which describes a layered nest of the system functions (Function Tree);
	\item Structure diagram (traditional class diagram);
	\item Behavior diagram which includes some parts of SDL language and DRAKON language popular in Russia.
\end{enumerate}

So, a developing system is described from three points of vision: function, structure and behavior. Each diagram element has a link to elements of two other diagrams. For example, you need to make changes in a behavior diagram. You can see which structure and function elements are affected. A lace of that kind is very important because it takes a long time to develop the real time system because demands are changing or a new team members want to change everything, etc. As you can see the system is alive.

Let’s describe behavior diagram more detailed. The real time system consists of hundreds or even thousands parallel processes which exchange massages. Often the process does nothing and does not occupy processor resource while being in some state from finite set of states. In behavior diagram behind an oval (which corresponds a state) goes several elements which mean message reception operators. When one of the messages comes a transition starts. During that transition several operators can be made, conditional operators as well. Massages can be sent, they can be sent to its own process as well. All that actions are finished when the transition comes to some state which can be transition’s initial state.

\captionsetup[figure]{name=Fig.}
\setcounter{figure}{6}

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.45\textwidth]{behaviorDiagramExample.png}
    \caption{Behavior diagram example}
    \label{image:behaviorDiagramExample}
\end{figure}

During developing real time systems our company has been applying graphic technology for many years. We have stored up plenty of methodological recommendations which prove its success in practice. Some methods and recommendations we borrowed from other technologies collecting experience and set of recommendations how to use graphic technologies properly. For example:
\begin{enumerate}
	\item Main algorithm branch must rest on a single vertical. Less likely conditional operators go to the right or show a mistake.
	\item Algorithms are to be described in a structural way. That means that any of the condition operator has one point of divergence, one point of variant point and its forbidden to go inside the cycle or condition operator etc.
	\item The cross of unit lines is forbidden.
\end{enumerate}

An important part of graphical reduction realization plays checking of correctness. For example for each send message a diagram must exist which includes operator to receive the massage. All three methodical rules (mentioned above) are in check as well. In behavior diagram an automatic code generation, data basis generation in structure diagram, tracers and debuggers are covered.

@@

\bibliographystyle{IEEEtran}
\bibliography{trikStudioEnglishExtended}
